A numerical study of the solution of X-Mode equations around the hybrid resonance

### 2015-05-04 report_clean/responce_reviewers.tex

\item {\textcolor{red}{p12}}

\item p12 Section 4.3: this explanation had been moved to the introduction

\item p12 Section 4.3.1

  True, but in this case there is no resonance, since $\delta(x)\equiv 0$. Hence $E_x=\frac{i\delta}{\alpha}E_y\equiv 0$, 
  and $E_y$ solves the Airy equation in the frequency domain. We added a small remark to Section 4.3.1 to underline this.

@@

\item p12 Equation (23): it had been removed

\item p14 Figures 8 and 9

Added the captions

\item p15 in Conclusion

  Indeed $P1$

### 2015-05-04 report_clean/responce_reviewers.tex

\item corrected the definition of the cold plasma dielectric tensor, to match the convention $\partial_t\rightarrow -i\omega$ (it had to be hermitian conjugate; 
this had been done everywhere, the corresponding corrections had been made in Table 1 and some figures)

\item corrected the definitions of $\alpha,\delta$ to comply with the definition of the cold plasma dielectric tensor of Stix

(more precisely, removed terms $\frac{\omega^2}{c^2}$ in 
front of them)

\item corrected the formulation of the lemma 2.3 on the well-posedness and added a remark after the lemma on the sign of $\nu$.

\item Section 4.1.1: corrected assumption on smoothness of $E_y^{\nu}$ in the section 'Numerical Experiments'.

### 2015-05-06 report_clean/intro.tex
+1
spotted a sign mistake

\urev{
We consider the wave propagation in the cold plasma that consists of particles of single species 
under a uniform in time background magnetic field $\mathbf{B}_0=(0,\;0,\; B_0)$. In two dimensions, in the plane 
perpendicular to the direction of the magnetic field, this process can be described by the time-dependent Maxwell system  \cite{Stix}
\begin{align}
\label{eq:main_system}
\begin{split}
-\varepsilon_0 \partial_t E_x +\partial_y H_z = J_x,\\
-\varepsilon_0 \partial_t E_y -\partial_x H_z = J_y,\\
\mu_0 \partial_t H_z + \partial_x E_y-\partial_y E_x= 0
\end{split}
\end{align}
coupled with the equations for the linear electronic current  $\J = eN_e(\mathbf{r}) \ubf$
\begin{align}
\begin{split}
\label{eq:electronmove}
m_e \partial_t u_x =\epsilon_0 e E_x+e B_0(\mathbf{r}) u_y -m_e \nu u_x,\\
m_e \partial_t u_y =\epsilon_0 e E_y-e B_0(\mathbf{r}) u_x -m_e \nu u_y,
\end{split}
\end{align}
where \mrev{$\nu\geq 0$} is the friction  between particles, $e<0$ is the charge of electrons, $m_e$ the electron mass and $N_e$ the electron density that in general 
depends on spatial variables and is uniform in time. A non-zero value of $\nu$ constitutes a basis for the limiting absorption principle. 
The unknowns are the electron velocity $\ubf$ and the electromagnetic field.

@@

Before proceeding, let us define the geometrical setting of the problem. We consider the frequency domain problem (\ref{eq:model_freq_domain}) posed in the domain $(-L,\;\infty)\times\mathbb{R},\; L>0$, with the 
 boundary conditions chosen as follows. At the left boundary of the domain, which represents the wall of the Tokamak, we pose Robin boundary conditions 
\be
\label{eq:boundary_conditions_intro}
curl \hat{\mathbf{E}} -i \lambda\hat{\mathbf{E}}\wedge \n = \hat{g}_{inc} =curl \E_{inc} -\imath\lambda\E_{inc}\wedge \n,
\ee
where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and \mrev{$\lambda\geq 0$} is 
the frequency of the antenna. We truncate the domain 
$(-L,\; \infty)\times\mathbb{R}$ to $(-L,\; H)\times\mathbb{R},\; H>0,$ and set on the right boundary $\operatorname{curl} \hat{\E} = 0$.

>>>>

\urev{
We consider the wave propagation in the cold plasma that consists of particles of single species 
under a uniform in time background magnetic field $\mathbf{B}_0=(0,\;0,\; B_0)$. In two dimensions, in the plane 
perpendicular to the direction of the magnetic field, this process can be described by the time-dependent Maxwell system  \cite{Stix}
\begin{align}
\label{eq:main_system}
\begin{split}
-\epsilon_0 \partial_t E_x +\partial_y H_z = J_x,\\
-\epsilon_0 \partial_t E_y -\partial_x H_z = J_y,\\
\mu_0 \partial_t H_z + \partial_x E_y-\partial_y E_x= 0
\end{split}
\end{align}
coupled with the equations for the linear electronic current  $\J = eN_e(\mathbf{r}) \ubf$
\begin{align}
\begin{split}
\label{eq:electronmove}
m_e \partial_t u_x =\epsilon_0 e E_x+e B_0(\mathbf{r}) u_y -m_e \nu u_x,\\
m_e \partial_t u_y =\epsilon_0 e E_y-e B_0(\mathbf{r}) u_x -m_e \nu u_y,
\end{split}
\end{align}
where \mrev{$\nu\geq 0$} is the friction  between particles, $e<0$ is the charge of electrons, $m_e$ the electron mass and $N_e$ the electron density that in general 
depends on spatial variables and is uniform in time. A non-zero value of $\nu$ constitutes a basis for the limiting absorption principle. 
The unknowns are the electron velocity $\ubf$ and the electromagnetic field.

@@

Before proceeding, let us define the geometrical setting of the problem. We consider the frequency domain problem (\ref{eq:model_freq_domain}) posed in the domain $(-L,\;\infty)\times\mathbb{R},\; L>0$, with the 
 boundary conditions chosen as follows. At the left boundary of the domain, which represents the wall of the Tokamak, we pose Robin boundary conditions 
\be
\label{eq:boundary_conditions_intro}
curl \hat{\mathbf{E}} \mrev{+}i \lambda\hat{\mathbf{E}}\wedge \n = \hat{g}_{inc} =curl \E_{inc} \mrev{+}\imath\lambda\E_{inc}\wedge \n,
\ee
where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and \mrev{$\lambda\geq 0$} is 
the frequency of the antenna. We truncate the domain 
$(-L,\; \infty)\times\mathbb{R}$ to $(-L,\; H)\times\mathbb{R},\; H>0,$ and set on the right boundary $\operatorname{curl} \hat{\E} = 0$.
